---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# invest.stock.db

<!-- badges: start -->
<!-- badges: end -->

The goal of invest.stock.db is to support the creation of a structured database for stock data to facilitate investment analysis.

## Installation

You can install the development version of yourpackage from GitHub:

``` r
# install.packages("remotes")
remotes::install_github("henrique-anatole/invest.data", dependencies = TRUE)

```

## Step by step example

The step by step below will allow you to create your own database. The invest.stock.db package will create it using duckdb and save it in a single file you can later use to connect and query. Therefore, the file name and path are the first variables to define, and this will be used to create the database connection.

```{r example}
# load the package
library(invest.stock.db)

# define the path and name of the database file
db_name <- "test_stock_db"
db_path <- file.path(tempdir(), db_name)

# create the database connection
db_con <- DBI::dbConnect(duckdb::duckdb(), dbdir = db_path, read_only = FALSE)

```

# Check the database structure and contents
```{r check_db, results='asis'}
# check the connection
is_valid_db_connection(db_con)

# List tables in the database. For this example, we expect to see nothing as we have not populated it yet.
tables <- DBI::dbListTables(db_con)
tables
```

# Symbols data

## Get basic data for all symbols

The first table to populate is the all_symbols table, which contains the list of stock symbols we will work with in the database. 

```{r symbols, results='asis'}

# get the list of symbols and save it to the all_symbols table
update_symbols_table(db_con, save_data = TRUE)

# Check the contents of the all_symbols table
all_symbols <- DBI::dbReadTable(db_con, "all_symbols")
head(all_symbols)

tables <- DBI::dbListTables(db_con)
dim(all_symbols)

# get the list of benchmark symbols and save it to the benchmark_symbols table
update_benchmarks(db_con)
# Check the contents of the benchmark_symbols table
benchmark_symbols <- DBI::dbReadTable(db_con, "benchmark_symbols")
head(benchmark_symbols)

# Load everything at once and check the tables again
all_symbols <- load_all_symbols(db_con)
head(all_symbols$all_symbols)
head(all_symbols$all_symbols_au)
head(all_symbols$all_symbols_br)
head(all_symbols$all_symbols_sp500)
head(all_symbols$all_benchmarks)
```

## Filtering the data

Next, I'll filter the symbols I will get more data for, because the database can get quite large if I try to get data for all symbols. 

```{r filter-symbols, results='asis'}
# Filter all SP500 symbols, plus the top 100 by rank for ASX and Bovespa
filtered_symbols <- all_symbols$all_symbols_sp500 %>% 
  dplyr::bind_rows(
    all_symbols$all_symbols_au %>% dplyr::slice_max(rank, n = 100)
  ) %>%
  dplyr::bind_rows(
    all_symbols$all_symbols_br %>% dplyr::slice_max(rank, n = 100)
  ) %>% 
  dplyr::bind_rows(
    all_symbols$all_benchmarks
  ) %>% 
  dplyr::distinct()

# Check the filtered symbols
head(filtered_symbols)

```

# Price time series data

Once I have the list of symbols I want to work with, I can proceed to get the price time series data for those symbols and populate the prices table in the database. I will start with the daily data.

```{r update-prices-daily, results='asis'}

symbols_to_get <- c("A8G.AX", "AAPL", "MSFT")
start_date <- as.character(Sys.Date() - lubridate::days(200))
interval <- "1d"
## Create the daily prices table in this new database
update_stock_prices(
db_con,
symbols_to_get,
start_date,
interval
)
## Check the contents of the daily_prices table
loaded_data <- DBI::dbGetQuery(db_con, "SELECT * FROM daily_prices")
# 2 Updating the existing table with new data
## Fake the data to be old
fake_old_date <- loaded_data %>% filter(open_time < as.character(Sys.Date() - 30))
## write back the fake old data to the database
DBI::dbWriteTable(db_con, "daily_prices", fake_old_date, overwrite = TRUE)
## Check the contents of the daily_prices table
symbols_before <- dbGetQuery(db_con,"SELECT symbol, MIN(open_time) as first_date, MAX(open_time) as last_date FROM daily_prices GROUP BY symbol")
## Now run the update function again to get the missing recent data
symbols_to_get <- c("A8G.AX", "AAPL", "MSFT", "GOOGL")
update_stock_prices(
db_con,
symbols_to_get,
start_date,
interval
)
## Check the table contents after updating
symbols_after <- dbGetQuery(db_con,"SELECT symbol, MIN(open_time) as first_date, MAX(open_time) as last_date FROM daily_prices GROUP BY symbol")

# compare before and after

```


```{r update-prices-hour, results='asis'}

symbols_to_get <- c("A8G.AX", "AAPL", "MSFT")
start_date <- as.character(Sys.Date() - lubridate::days(7))
interval <- "1h"

load_stock_timeseries(symbols = "A8G.AX",
   interval="1m",
   start_date="2024-09-03",
   end_date="2024-09-04")

riingo::is_supported_ticker("CBA")

## Create the daily prices table in this new database
update_stock_prices(
db_con,
symbols_to_get,
start_date,
interval
)
## Check the contents of the hourly_prices table
loaded_data <- DBI::dbGetQuery(db_con, "SELECT * FROM hourly_prices")
# 2 Updating the existing table with new data
## Fake the data to be old
fake_old_date <- loaded_data %>% filter(open_time < as.character(Sys.Date() - 4))
## write back the fake old data to the database
DBI::dbWriteTable(db_con, "hourly_prices", fake_old_date, overwrite = TRUE)
## Check the contents of the hourly_prices table
symbols_before <- dbGetQuery(db_con,"SELECT symbol, MIN(open_time) as first_date, MAX(open_time) as last_date FROM hourly_prices GROUP BY symbol")
## Now run the update function again to get the missing recent data
symbols_to_get <- c("A8G.AX", "AAPL", "MSFT", "GOOGL")
update_stock_prices(
db_con,
symbols_to_get,
start_date,
interval
)
## Check the table contents after updating
symbols_after <- dbGetQuery(db_con,"SELECT symbol, MIN(open_time) as first_date, MAX(open_time) as last_date FROM hourly_prices GROUP BY symbol")


# disconnect when done
DBI::dbDisconnect(db_con, shutdown = TRUE)

```





