---
title: "my_new_stock_db"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my_new_stock_db}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(invest.stock.db)
```

# Introduction
This vignette demonstrates how to create a new stock database using the `invest.stock.db` package. We will walk through the steps of setting up a new database, populating it with stock data, and performing basic queries.
# Setting Up a New Stock Database
To create a new stock database, we first need to define the structure of our database. This includes specifying the tables and fields that will hold our stock data.
```{r create_db}
# Create a new stock database using duckdb
# db_name <- "test_stock_db"
# db_path <- file.path(tempdir(), db_name)
# con <- DBI::dbConnect(duckdb::duckdb(), dbdir = db_path, read_only = FALSE)

```

# Check the database structure and contents
```{r check_db, results='asis'}
# # check the connection
# if (!grepl("connection", class(con))) {
#     stop("Failed to connect to the database.")
#   }

# # List tables in the database
# tables <- DBI::dbListTables(con)
# # check if all_symbols table exists
# if (!"all_symbols" %in% tables) {
#     stop("Table 'all_symbols' does not exist in the database.")
#   }

# # get the list of symbols
# all_symbols <- invest.stock.db::get_symbols(con)

```

# Populate the Database with Stock Data

```{r populate_db}


```

